The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-16 talk/vmil2012/paper.tex
remove orphaned reference to figure

After tracing has been finished the trace is optimized.
During optimization a large percentage of operations can be removed (Figure~\ref{fig:benchmarks}).
In the process the resume data is transformed into its final, compressed form.
The rationale for not compressing the resume data during tracing
is that a lot of guards will be optimized away.
For them, the compression effort would be lost.

>>>>

After tracing has been finished the trace is optimized.
During optimization a large percentage of operations can be removed. \todo{add a reference to the figure showing the optimization rates?}
In the process the resume data is transformed into its final, compressed form.
The rationale for not compressing the resume data during tracing
is that a lot of guards will be optimized away.
For them, the compression effort would be lost.
